EinsteinPy: A Community Python Package for General Relativity

### 2020-05-18 paper.tex
Last Iteration

@@

  School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, Mandi, Himachal Pradesh, India

@@

@@

\subsection{Rays}
The rays module of EinsteinPy tries to focus on how light behaves around heavy mass objects and the 
The plotting module throughout the applications follow a very consistent API. 
The major functionality this module provides is the utility functions for carrying out shadow related computations for different black hole spacetime. The module has natural data types to efficiently store impact parameters and use them in further computations related to wavelength shifts, turning point etc. The specific assumptions about the accretion process and the emission mechanisms are in accordance with that given in \citep{Bambi_2013}.
The module also provide functionalities related to intensities of blue shifted and red shifted rays above and below the critical impact parameters. For mathematical formalism of the above computations refer to the \citep{Bambi_2013} and \citep{Shaikh_2018}.

>>>>

Nihar Gupte\inst{\ref{inst:uf}}
Gagan Shenoy\inst{\ref{inst:manipalcs}}
Micky Yun Chan\inst{\ref{inst:lat}}

@@

  School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, Mandi, Himachal Pradesh, India 175005

@@

  Department of Physics, University of Florida, Gainesville, FL, USA
  \label{inst:uf}
  Latvia University of Life Sciences and Technologies, Lielā iela 2, Jelgava, LV-3001, Latvia
  \label{inst:lat}

@@

\subsection{Rays}
The rays module of EinsteinPy tries to focus on how light behaves around heavy mass object.
The major functionality this module provides is the utility functions for carrying out shadow related computations for different black hole spacetimes. The module has natural data types to efficiently store impact parameters and use them in further computations related to wavelength shifts, turning point etc. The specific assumptions about the accretion process and the emission mechanisms are in accordance with that given in \citep{Bambi_2013}.
The module also provide functionalities related to intensities of blue shifted and red shifted rays above and below the critical impact parameters. For mathematical formalism of the above computations refer to the \citep{Bambi_2013} and \citep{Shaikh_2018}.

This module is under heave developement since past February 2020, and we expect significant contributions to this module thanks to Google Summer of Code 2020.
